|

### 2023-04-26 manuscript/Chapter2-appendix1.Rmd
update tables in all .Rmd files

output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: ecology.csl
---

@@

# Fixed effects table
results <- data.table(
  round(summary(fit)$fixed, digits = 3)[, 1:4],
  keep.rownames = TRUE
)

@@

tabs1f <- tabs1 %>%
  flextable(col_keys = my_header$col_keys) %>%
  set_header_df(mapping = my_header, key = "col_keys") %>%
  my_theme() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top", part = "body") %>%
  align(align = "left", part = "all", j = c(1, 2)) %>%
  align(align = "center", part = "all", j = 3) %>%
  align(align = "center", part = "all", j = 4) %>%
  align(align = "center", part = "all", j = 5) %>%
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299"
    ),
    ref_symbols = " "
  ) %>%
  set_caption(
    tabs1,
    caption = "Fixed effects table on the mean part of the model",
    style = "Table Caption"
  ) %>%
  fontsize(size = 10, part = "all") %>%
  fontsize(size = 12, part = "footer") %>%
  font(fontname = "Times New Roman", part = "all")

@@

tabs2f <- tabs2 %>%
  flextable(col_keys = my_header$col_keys) %>%
  set_header_df(mapping = my_header, key = "col_keys") %>%
  my_theme() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top", part = "body") %>%
  align(align = "left", part = "all", j = c(1, 2)) %>%
  align(align = "center", part = "all", j = 3) %>%
  align(align = "center", part = "all", j = 4) %>%
  align(align = "center", part = "all", j = 5) %>%
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299"
    ),
    ref_symbols = " "
  ) %>%
  set_caption(
    tabs2,
    caption = "Fixed effects table on the dispersion part of the model",
    style = "Table Caption"
  ) %>%
  fontsize(size = 10, part = "all") %>%
  fontsize(size = 12, part = "footer") %>%
  font(fontname = "Times New Roman", part = "all")

>>>>

output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references2.bib
csl: ecology.csl
---

@@

# Fixed effects table
results <- data.table(
  round(summary(fit)$fixed, digits = 2)[, 1:4],
  keep.rownames = TRUE
)

@@

tabs1f <- tabs1 %>%
  flextable(col_keys = my_header$col_keys) %>%
  set_header_df(mapping = my_header, key = "col_keys") %>%
  my_theme() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top", part = "body") %>%
  align(align = "left", part = "all", j = c(1, 2)) %>%
  align(align = "center", part = "all", j = 3) %>%
  align(align = "center", part = "all", j = 4) %>%
  align(align = "center", part = "all", j = 5) %>%
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299 (i.e. group in the main text)"
    ),
    ref_symbols = " "
  ) %>%
  set_caption(
    tabs1,
    caption = "Table S1. Fixed effects table on the mean part of the DHMLM comparing random groups of players with different matches played to the group presented in the main text.",
    style = "Table Caption"
  ) %>%
  fontsize(size = 10, part = "all") %>%
  fontsize(size = 12, part = "footer") %>%
  font(fontname = "Times New Roman", part = "all")

@@

tabs2f <- tabs2 %>%
  flextable(col_keys = my_header$col_keys) %>%
  set_header_df(mapping = my_header, key = "col_keys") %>%
  my_theme() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top", part = "body") %>%
  align(align = "left", part = "all", j = c(1, 2)) %>%
  align(align = "center", part = "all", j = 3) %>%
  align(align = "center", part = "all", j = 4) %>%
  align(align = "center", part = "all", j = 5) %>%
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299 (i.e. group in the main text)"
    ),
    ref_symbols = " "
  ) %>%
  set_caption(
    tabs2,
    caption = "Table S2. Fixed effects table on the dispersion part of the DHMLM comparing random groups of players with different matches played to the group presented in the main text.",
    style = "Table Caption"
  ) %>%
  fontsize(size = 10, part = "all") %>%
  fontsize(size = 12, part = "footer") %>%
  font(fontname = "Times New Roman", part = "all")

### 2023-04-26 manuscript/Chapter2-appendix3.Rmd
update tables in all .Rmd files

---
title: |
     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame: \
    Appendix 3
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: ecology.csl
---

@@

# Round values to 3 digits
eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 3)]

@@

# Paste upper and lower ci with estimate
eff_tab[, estimate := paste(format(Estimate, digits = 3), "(")]
eff_tab[, estimate := paste(estimate, format(lower_ci, digits = 3), sep = "")]
eff_tab[, estimate := paste(estimate, ",", sep = "")]
eff_tab[, estimate := paste(estimate, format(upper_ci, digits = 3), sep = " ")]
eff_tab[, estimate := paste(estimate, ")", sep = "")]
eff_tab[, c("Estimate", "lower_ci", "upper_ci") := NULL]

@@

# Custom theme
my_theme <- function(x, ...) {
  x <- colformat_double(x, big.mark = " ",
                        decimal.mark = ".",
                        digits = 3)
  x <- set_table_properties(x, layout = "fixed")
  x <- border_remove(x)
  std_border <- fp_border(width = 1, color = "black")
  x <- hline_top(x, part = "all", border = std_border)
  x <- hline_bottom(x, part = "all", border = std_border)
  autofit(x)
}

@@

  # Table caption
  set_caption(
    caption = "Table S1. Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
    style = "Table Caption"
  ) %>%

  # Font options
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  fontsize(size = 12, part = "footer") %>%
  width(j = c(2, 3, 4, 5), width = 3.7, unit = "cm") %>%
  width(j = 1, width = 3.2, unit = "cm")

@@

ranef_tab <- unique(ranef_tab[, .(parameter, mean, lower_ci, upper_ci)])
ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], 3)]

@@

# Paste upper and lower ci with estimate
ranef_tab[, estimate := paste(format(mean, digits = 3), "(")]
ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 3), sep = "")]
ranef_tab[, estimate := paste(estimate, ",", sep = "")]
ranef_tab[, estimate := paste(estimate, format(upper_ci, digits = 3), sep = " ")]
ranef_tab[, estimate := paste(estimate, ")", sep = "")]
ranef_tab[, c("mean", "lower_ci", "upper_ci") := NULL]

@@

# Reorder rows
table <- ranef_tab[c(1:5, 6:9)]

@@

# Custom theme
my_theme <- function(x, ...) {
  x <- colformat_double(x, big.mark = " ",
                        decimal.mark = ".",
                        digits = 3)
  x <- set_table_properties(x, layout = "fixed")
  x <- border_remove(x)
  std_border <- fp_border(width = 1, color = "black")
  x <- hline_top(x, part = "all", border = std_border)
  x <- hline_bottom(x, part = "all", border = std_border)
  autofit(x)
}

@@

  # Add table caption
  set_caption(
    caption = "Table 3. Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
    style = "Table Caption"
  ) %>%

  # Font options
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  fontsize(size = 12, part = "footer") %>%
  width(j = c(2, 3, 4, 5), width = 3.7, unit = "cm") %>%
  width(j = 1, width = 3.2, unit = "cm")

@@

```{r figS3, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM. The test is displayed on the y axis (i.e. whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience level groups that are being compared."}

>>>>

---
title: |
     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame: \
     Appendix 3

output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references2.bib
csl: ecology.csl
---

@@

# Round values to 3 digits
eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 2)]

@@

# Paste upper and lower ci with estimate
eff_tab[, estimate := paste(format(Estimate, digits = 2), "(")]
eff_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
eff_tab[, estimate := paste(estimate, ",", sep = "")]
eff_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
eff_tab[, estimate := paste(estimate, ")", sep = "")]
eff_tab[, c("Estimate", "lower_ci", "upper_ci") := NULL]

@@

# Custom theme
my_theme <- function(x, ...) {
  x <- colformat_double(x, big.mark = " ",
                        decimal.mark = ".",
                        digits = 2)
  x <- border_remove(x)
  std_border <- fp_border(width = 1, color = "black")
  x <- hline_top(x, part = "all", border = std_border)
  x <- hline_bottom(x, part = "all", border = std_border)
  x <- width(x, j = 1, width = 2.84, unit = "cm")
  x <- width(x, j = 2, width = 3.78, unit = "cm")
  x <- width(x, j = c(3:5), width = 3.3, unit = "cm")
}

@@

  # Table caption
  set_caption(
    caption = "Table S1. Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success. The coefficients are from the model that includes the outlier.",
    style = "Table Caption"
  ) %>%

  # Font options
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  fontsize(size = 12, part = "footer")

@@

ranef_tab <- unique(ranef_tab[, .(parameter, mean, lower_ci, upper_ci)])
ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], digits = 2)]

@@

# Paste upper and lower ci with estimate
ranef_tab[, estimate := paste(format(mean, digits = 2), "(")]
ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
ranef_tab[, estimate := paste(estimate, ",", sep = "")]
ranef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
ranef_tab[, estimate := paste(estimate, ")", sep = "")]
ranef_tab[, c("mean", "lower_ci", "upper_ci") := NULL]

@@

# Reorder rows
table <- ranef_tab[c(2:9, 1)]

@@

# Custom theme
my_theme <- function(x, ...) {
  x <- colformat_double(x, big.mark = " ",
                        decimal.mark = ".",
                        digits = 2)
  x <- set_table_properties(x, layout = "autofit")
  x <- border_remove(x)
  std_border <- fp_border(width = 1, color = "black")
  x <- hline_top(x, part = "all", border = std_border)
  x <- hline_bottom(x, part = "all", border = std_border)
  autofit(x)
}

@@

  # Add table caption
  set_caption(
    caption = "Table S2. Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success. The coefficients are from the model that includes the outlier.",
    style = "Table Caption"
  ) %>%

  # Font options
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  fontsize(size = 12, part = "footer")

tab3 <- autofit(tab3)

@@

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM. The test is displayed on the y axis (i.e. whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience level groups that are being compared."}
